%-----------------------------------------------------------------------------------------------------------------------------------------------%
%	The MIT License (MIT)
%
%	Copyright (c) 2021 Jitin Nair
%
%	Permission is hereby granted, free of charge, to any person obtaining a copy
%	of this software and associated documentation files (the "Software"), to deal
%	in the Software without restriction, including without limitation the rights
%	to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
%	copies of the Software, and to permit persons to whom the Software is
%	furnished to do so, subject to the following conditions:
%	
%	THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
%	IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
%	FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
%	AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
%	LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
%	OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN
%	THE SOFTWARE.
%	
%
%-----------------------------------------------------------------------------------------------------------------------------------------------%

%----------------------------------------------------------------------------------------
%	DOCUMENT DEFINITION
%----------------------------------------------------------------------------------------

% article class because we want to fully customize the page and not use a cv template
\documentclass[a4paper,12pt]{article}

%----------------------------------------------------------------------------------------
%	FONT
%----------------------------------------------------------------------------------------

% % fontspec allows you to use TTF/OTF fonts directly
% \usepackage{fontspec}
% \defaultfontfeatures{Ligatures=TeX}

% % modified for ShareLaTeX use
% \setmainfont[
% SmallCapsFont = Fontin-SmallCaps.otf,
% BoldFont = Fontin-Bold.otf,
% ItalicFont = Fontin-Italic.otf
% ]
% {Fontin.otf}

%----------------------------------------------------------------------------------------
%	PACKAGES
%----------------------------------------------------------------------------------------
\usepackage{url}
\usepackage{parskip} 	

%other packages for formatting
\RequirePackage{color}
\RequirePackage{graphicx}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[scale=0.9]{geometry}

%tabularx environment
\usepackage{tabularx}

%for lists within experience section
\usepackage{enumitem}

% centered version of 'X' col. type
\newcolumntype{C}{>{\centering\arraybackslash}X} 

%to prevent spillover of tabular into next pages
\usepackage{supertabular}
\usepackage{tabularx}
\newlength{\fullcollw}
\setlength{\fullcollw}{0.47\textwidth}

%custom \section
\usepackage{titlesec}				
\usepackage{multicol}
\usepackage{multirow}

%CV Sections inspired by: 
%http://stefano.italians.nl/archives/26
\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{10pt}{10pt}

%for publications
\usepackage[style=authoryear,sorting=ynt, maxbibnames=2]{biblatex}

%Setup hyperref package, and colours for links
\usepackage[unicode, draft=false]{hyperref}
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour,linkcolor=linkcolour}
\addbibresource{citations.bib}
\setlength\bibitemsep{1em}

%for social icons
\usepackage{fontawesome5}

%debug page outer frames
%\usepackage{showframe}


% job listing environments
\newenvironment{jobshort}[2]
    {
    \begin{tabularx}{\linewidth}{@{}l X r@{}}
    \textbf{#1} & \hfill &  #2 \\[3.75pt]
    \end{tabularx}
    }
    {
    }

\newenvironment{joblong}[2]
    {
    \begin{tabularx}{\linewidth}{@{}l X r@{}}
    \textbf{#1} & \hfill &  #2 \\[3.75pt]
    \end{tabularx}
    \begin{minipage}[t]{\linewidth}
    \begin{itemize}[nosep,after=\strut, leftmargin=1em, itemsep=3pt,label=--]
    }
    {
    \end{itemize}
    \end{minipage}    
    }



%----------------------------------------------------------------------------------------
%	BEGIN DOCUMENT
%----------------------------------------------------------------------------------------
\begin{document}

% non-numbered pages
\pagestyle{empty} 

%----------------------------------------------------------------------------------------
%	TITLE
%----------------------------------------------------------------------------------------

% \begin{tabularx}{\linewidth}{ @{}X X@{} }
% \huge{Your Name}\vspace{2pt} & \hfill \emoji{incoming-envelope} email@email.com \\
% \raisebox{-0.05\height}\faGithub\ username \ | \
% \raisebox{-0.00\height}\faLinkedin\ username \ | \ \raisebox{-0.05\height}\faGlobe \ mysite.com  & \hfill \emoji{calling} number
% \end{tabularx}

\begin{tabularx}{\linewidth}{@{} C @{}}
\Huge{Vibhuti Dureja} \\[7.5pt]
\href{https://github.com/vibhutidureja}{\raisebox{-0.05\height}\faGithub\ vibhutidureja} \ $|$ \ 
\href{https://linkedin.com/in/vibhuti-dureja}{\raisebox{-0.05\height}\faLinkedin\ vibhuti-dureja} \ $|$ \
\href{mailto:vd20075834@gmail.com}{\raisebox{-0.05\height}\faEnvelope \ vd20075834@gmail.com} \ $|$ \ 
\href{tel:+918168504716}{\raisebox{-0.05\height}\faMobile \ +91 81685 04716} \\
\end{tabularx}

%----------------------------------------------------------------------------------------
% EXPERIENCE SECTIONS
%----------------------------------------------------------------------------------------

%Interests/ Keywords/ Summary
\section{Summary}
Motivated and curious first-year \textbf{B.Tech Computer Engineering} student at \textbf{NIT Delhi} with a strong foundation in programming, data structures, and algorithms. Passionate about technology, innovation, and problem solving. Enthusiastic about exploring opportunities that combine analytical thinking and creativity — particularly in software development and research.

%Experience
\section{Work Experience}


\begin{jobshort}{Training and Placement Cell Coordinator}{March 2025 - present}
\begin{itemize}[nosep,after=\strut, leftmargin=1em, itemsep=3pt,label=--]
    \item Coordinated between recruiters and the student body, streamlining placement-related communication and schedules.
    \item Drafted professional mails, announcements, and placement briefs improving clarity and engagement.
    \item Worked with the team to organize pre-placement talks, aptitude sessions, and one-to-one interviews for students.
\end{itemize}
\end{jobshort}


\begin{joblong}{Volunteer - Think India}{Nov 2024 - present}
\item Contributed actively to discussions, seminars, and awareness drives on national and student-centric issues.
\item Organized a Teachers’ Day seminar, managing coordination, event flow, and content planning.
\item Secured 3rd position in an inter-college debate competition organized by Think India for exceptional articulation and critical reasoning.
\end{joblong}
  
%Projects
\section{Projects}

\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{College Website} & \hfill \href{https://college-website-three-henna.vercel.app/}{Link to Demo} \\[3.75pt]
\multicolumn{2}{@{}X@{}}{Tech Stack: HTML, CSS, JavaScript
Developed a responsive and interactive website to provide information about college departments, events, and facilities.
Designed user-friendly navigation with sections like About, Courses, Faculty, and Contact.
Implemented form validation using JavaScript for smooth data entry and submission.
Focused on accessibility and clean UI design to enhance user experience.}  \\
\end{tabularx}

\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{Expense Tracker} & \hfill \href{https://expense-tracker-nine-black-25.vercel.app/}{Link to Demo} \\[3.75pt]
\multicolumn{2}{@{}X@{}}{Tech Stack: HTML, CSS, JavaScript (Local Storage)
Built a fully functional expense tracking system to record, categorize, and analyze daily expenses.
Integrated features like filtering, category management, dark/light mode toggle, and real-time balance calculation.
Used Local Storage for data persistence without external databases.
Implemented dynamic charts and visual summaries to track spending patterns.
Focused on responsive design and efficient code structure for scalability.}  \\
\end{tabularx}

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------
\section{Education}
\begin{tabularx}{\linewidth}{@{}l X@{}}
2024 - 2028 & Bachelor's Degree at \textbf{National Institute of Technology Delhi} \hfill (CGPA: 8.6/10.0) \\ 

2024 & Class 12th Some Board \hfill  (92.4%) \\

2022 & Class 10th CBSE \hfill  (96.8%) \\
\end{tabularx}

%----------------------------------------------------------------------------------------
%	SKILLS
%----------------------------------------------------------------------------------------
\section{Skills}
\begin{tabularx}{\linewidth}{@{}l X@{}}
\textbf{Programming Languages} & C, Java, JavaScript \\ 
\textbf{Web Technologies} & HTML, CSS, Node.js, Express.js \\ 
\textbf{Core Areas} & Data Structures and Algorithms (DSA), Object-Oriented Programming (OOP) \\ 
\textbf{Tools \& Concepts} & Git, GitHub, REST APIs, Basic Machine Learning (Python, NumPy, Pandas, Scikit-learn) \\ 
\end{tabularx}

\vfill
\center{\footnotesize Last updated: \today}

\end{document}
